Size-environment interaction

### 2021-01-15 analysis/supplementary-materials/size-environment_interaction.Rmd
filter out unrealisticly tiny plants

```{r data, echo=TRUE}
demog <-
  read_csv(
    here("analysis", "data", "derived_data", "ha_survey.csv"),
    col_names = TRUE,
    cols(plot = col_character(),
         bdffp_reserve_no = col_character())
  )
demog <-
  demog %>%
  filter(ht < 200, ht_next < 200) %>% 
  filter(shts > 0, shts_next > 0, ht > 0, ht_next > 0) %>% 
  mutate(size = shts*ht, size_next = shts_next*ht_next, log_size = log(size), log_size_next = log(size_next))
```

>>>>

```{r data, echo=TRUE}
demog <-
  read_csv(
    here("analysis", "data", "derived_data", "ha_survey.csv"),
    col_names = TRUE,
    cols(plot = col_character(),
         bdffp_reserve_no = col_character())
  )
demog <-
  demog %>%
  filter(ht < 200, ht_next < 200) %>% 
  filter(shts > 0, shts_next > 0, ht >= 1, ht_next >= 1) %>% 
  mutate(size = shts*ht, size_next = shts_next*ht_next, log_size = log(size), log_size_next = log(size_next))
```
